---
title: "riskr"
output:
  html_document:
    keep_md: yes
    toc: yes
  md_document:
    toc: true
---
<!-- README.md is generated from README.Rmd -->

```{r, echo = FALSE}
library("printr")
options(digits = 3, knitr.table.format = "markdown")
knitr::opts_chunk$set(collapse = TRUE, comment = ">", warning = FALSE,
                      fig.path = "vignettes/figures/", fig.width = 7,
                      fig.align = "center", dpi = 72)
```

## Introduction

The `riskr` package facilitate *credit scoring* tasks such as measure the scores/models performance and make easy the scoring modelling process.

There are function to:

 1. Measure in a simple way the performance of models via wrapper or shortcuts from ROCR functions.
 2. Visualize relationships between variables.
 4. Compute usual values in the credit scoring PSI, WOE, IV, KS, AUCROC, among others.
 5. Make easier the scoring modelling process. 

## Assumption

`riskr` assume the target variable is *binary* with numeric values: 0 and 1. Usually 1 means the characteristic of interest.

## Installation

You can install the latest development version from github with:

```{r, eval=FALSE}
devtools::install_github("jbkunst/riskr")
```

## Functions

Usually we have a data frame with a *target* variable and a *score* (or probability) like this:

```{r}
library("riskr")

data("predictions")

head(predictions)

str(predictions)

score <- predictions$score

target <- predictions$target
```

### Performance Indicators

The main statistics or indicators are KS, AUCROC so:

```{r}
ks(score, target)

aucroc(score, target)

gini(score, target)

score_indicators(score, target)
```

There are some functions to plot the score/model performance (based on ggplot package).

```{r}
plot_roc(score, target)

plot_gain(score, target)

plot_ks(1000 * score, target) +
  ggthemes::theme_hc() +
  ggtitle(sprintf("The KS statistics is %.0f%%", 100 * ks(score, target)))
```

### Odds Tables

The odds tables are other way to show how a score/model performs.

```{r}
score <- round(predictions$score * 1000)

odds_table(score, target, nclass = 5) # default is (nclass =) 10 groups of equal size

odds_table(score, target, breaks = c(0, 300, 700, 999))
```

### Confusion Matrix

The `conf_matrix` function return a list with the next elements:

```{r}
score_cat <- ifelse(score < 500, 0, 1)

cm <- conf_matrix(score_cat, target)
```

- The confusion matrix:
```{r}
cm$confusion.matrix
```

- The confusion matrix statistics
```{r}
cm$indicators

cm$indicators.t
```


### Bivariate Tables

```{r}
data("credit")

str(credit)

ft(credit$marital_status)

bt(credit$marital_status, credit$bad)

library("ggplot2")

credit$age_bin <- cut_interval(credit$age, 4)

bt(credit$age_bin, credit$bad)

plot_bt(credit$age_bin, credit$bad) + ggtitle("Age")

plot_bt(credit$flag_res_phone, credit$bad,
        count.labels = TRUE, target.labels = TRUE) +
  ggtitle("Flag Response Phone")

```

## Related work

1. [woe](github.com/tomasgreif/woe) package by [tomasgreif](github.com/tomasgreif)
2. [smbinning](http://cran.r-project.org/web/packages/smbinning) package by [Herman Jopia](github.com/hjopia). [Github repository](https://github.com/cran/smbinning).
