---
title: "riskr"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data frames}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, echo = FALSE, warning=FALSE}
library("riskr")
library("ggplot2")
library("ggthemes")
options(digits = 3, knitr.table.format = "markdown")
knitr::opts_chunk$set(collapse = TRUE, warning = FALSE,
                      fig.path = "vignettes/figures/",
                      fig.width = 6, fig.height = 6,
                      fig.align = "center", dpi = 72)

theme_set(theme_fivethirtyeight(base_size = 11) +
            theme(axis.title = element_text(colour = "grey30"),
                  axis.title.y = element_text(angle = 90),
                  strip.background = element_rect(fill = "#434348"),
                  strip.text = element_text(color = "#F0F0F0"),
                  plot.title = element_text(face = "plain", size = structure(1.2, class = "rel"))))
update_geom_defaults("line", list(colour = "#434348", size = 1.05))
update_geom_defaults("point", list(colour = "#434348", size = 3))
update_geom_defaults("bar", list(fill = "#7cb5ec"))
update_geom_defaults("text", list(size = 4, colour = "gray30"))
```

[![travis-status](https://api.travis-ci.org/jbkunst/riskr.svg)](https://travis-ci.org/jbkunst/riskr)
[![Coverage Status](https://coveralls.io/repos/jbkunst/riskr/badge.svg?branch=master&service=github)](https://coveralls.io/github/jbkunst/riskr?branch=master)


## Introduction

The `riskr` package facilitate *credit scoring* tasks such as measure the scores/models performance and make easy the scoring modelling process.

There are function to:

 1. Measure in a simple way the performance of models via wrappers/shortcuts from ROCR functions.
 2. Visualize relationships between variables.
 4. Compute usual values in the credit scoring PSI, WOE, IV, KS, AUCROC, among others.
 5. Make easier the modelling and validation process. 

## Assumptions

`riskr` assume the target variable is *binary* with numeric values: 0 and 1. Usually 1 means the characteristic of interest.

## Installation

You can install the latest development version from github with:

```{r, eval=FALSE}
devtools::install_github("jbkunst/riskr")
```

## Functions

### Performance Indicators & Plots

Usually we have a data frame with a *target* variable and a *score* (or probability) like this:

```{r}
library("riskr")

data("predictions")

head(predictions)

score <- predictions$score

target <- predictions$target
```

The main statistics or indicators are KS, AUCROC so:
